---
title: "agricultural land use change analysis"
format: html
editor: visual
---

## Running Code

**Load Libraries**

```{r}
library(sf)
library(tidyverse)
library(here)
library(mapview)
```

**Read in data**

```{r}
ag_2015 <- st_read(
  here("data", "Agricultural_Land_Use_-_2015_Baseline.geojson")
)
```

**Read in data**

```{r}
ag_2020 <- st_read(
  here("data","Agricultural_Land_Use_-_2020_Update.geojson" )
)
```

**Make a map**

```{r}
mapview(ag_2015, zcol = "cropcatego")
```

```{r}
unique(ag_2015$cropcatego)
```

R color brewer can enhance this

Distribution of Acreage

```{r}
ggplot(ag_2015, aes(x = acreage)) +
  geom_histogram() +
  theme_bw() +
  facet_wrap(~island, scales = "free_y")
```

**Questions:**

How have things changed, has acreage changed from Ag Land from 2015-2020?

Did we add/loose ag land acreage between 2015 and 2020?

```{r}
sum(ag_2015$acreage)
sum(ag_2020$acreage)
```

```{r}
sum_2015_acreage <- sum(ag_2015$acreage)
sum_2020_acreage <- sum(ag_2020$acreage)
```

What has that land been converted to?

one map of lost ag land between 2015 and 2020?

ag land ownership

By what crop?

NDVI in lost ag land

soil type
